---
title: "Reproducible Research: Peer Assessment 1"
output: html_document
---

Loading and processing the data

```{r}
setwd("C:/Users/Daddy 2/Documents/Reproducible Research/Reproducible-Research")
data <- read.csv("activity.csv", colClasses = c("integer", "Date", "factor"))
data$month <- as.numeric(format(data$date, "%m"))
noNA <- na.omit(data)
rownames(noNA) <- 1:nrow(noNA)
head(noNA)
dim(noNA)
library(ggplot2)
```

What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

Make a histogram of the total number of steps taken each day

```{r}
ggplot(noNA, aes(date, steps)) + geom_bar(stat = "identity", colour = "steelblue", fill = "steelblue", width = 0.7) + facet_grid(. ~ month, scales = "free") + labs(title = "Histogram of Total Number of Steps Taken Each Day", x = "Date", y = "Total number of steps")
```
Calculate and report the mean and median total number of steps taken per day
Mean total number of steps taken per day:
```{r}
totalSteps <- aggregate(noNA$steps, list(Date = noNA$date), FUN = "sum")$x
mean(totalSteps)
```
Median total number of steps taken per day:

```{r}
median(totalSteps)
```
What is the average daily activity pattern?

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
'''{r}
avgSteps <- aggregate(noNA$steps, list(interval = as.numeric(as.character(noNA$interval))), FUN = "mean")
names(avgSteps)[2] <- "meanOfSteps"

ggplot(avgSteps, aes(interval, meanOfSteps)) + geom_line(color = "steelblue", size = 0.8) + labs(title = "Time Series Plot of the 5-minute Interval", x = "5-minute intervals", y = "Average Number of Steps Taken")
```
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
'''{r}
avgSteps[avgSteps$meanOfSteps == max(avgSteps$meanOfSteps), ]
'''
Inputing missing values

The total number of rows with NAs:
'''{r}
sum(is.na(data))
'''
Create a new dataset that is equal to the original dataset but with the missing data filled in.
'''{r}
newData <- data 
for (i in 1:nrow(newData)) {
    if (is.na(newData$steps[i])) {
        newData$steps[i] <- avgSteps[which(newData$interval[i] == avgSteps$interval), ]$meanOfSteps
    }
}

head(newData)
sum(is.na(newData))
'''
Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.
'''{r}
ggplot(newData, aes(date, steps)) + geom_bar(stat = "identity",
                                             colour = "steelblue",
                                             fill = "steelblue",
                                             width = 0.7) + facet_grid(. ~ month, scales = "free") + labs(title = "Histogram of Total Number of Steps Taken Each Day (no missing data)", x = "Date", y = "Total number of steps")
'''
Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?
'''{r}
newMean <- mean(newTotalSteps)
newMean
newMedian <- median(newTotalSteps)
newMedian
oldMean <- mean(totalSteps)
oldMedian <- median(totalSteps)
newMean - oldMean
newMedian - oldMedian
'''
Are there differences in activity patterns between weekdays and weekends?

Create a new factor variable in the dataset with two levels -- "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.
'''{r}
head(newData)
newData$weekdays <- factor(format(newData$date, "%A"))
levels(newData$weekdays)
levels(newData$weekdays) <- list(weekday = c("Monday", "Tuesday",
                                             "Wednesday", 
                                             "Thursday", "Friday"),
                                 weekend = c("Saturday", "Sunday"))
levels(newData$weekdays)
table(newData$weekdays)
'''
Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).
'''{r}
avgSteps <- aggregate(newData$steps, 
                      list(interval = as.numeric(as.character(newData$interval)), 
                           weekdays = newData$weekdays),
                      FUN = "mean")
names(avgSteps)[3] <- "meanOfSteps"
library(lattice)
xyplot(avgSteps$meanOfSteps ~ avgSteps$interval | avgSteps$weekdays, 
       layout = c(1, 2), type = "l", 
       xlab = "Interval", ylab = "Number of steps")
'''